Applying Spatio-temporal Scan Statistics and Spatial Autocorrelation Statistics to identify Covid-19 clusters in the world.

### 2021-01-12 Notebooks/paper_covid.rmd
Update paper_covid.rmd

  In April global cases of Covid-19 reached 1 million, in the same month the world also reached 3 million cases $\!\!^3$, with an exponential growth in the number of infections, the Global Moran's I was also very high for the number of deaths per inhabitant, while local spatial association was strong only in Europe, the boxmap **(Picture 3)** shows that all areas identified with local dependence for the number of deaths per inhabitant were either HH (High-High) clusters in April or HL (High-Low) clusters after April, which means that in general locations with a high number of deaths were close to other areas that also had a high number of deaths. Even though April was a very concerning month to the international community, global spatial autocorrelation on the number of cases per inhabitant only started to grow higher than IM>0.50 in October, but the boxmaps for the number of infections show the same trend that happened for the number of deaths **(Picture 4)**, when looking to the *LISA* map **(Picture 2)**.

>>>>

  In April global cases of Covid-19 reached 1 million, in the same month the world also reached 3 million cases $\!\!^3$, with an exponential growth in the number of infections, the Global Moran's I was also very high for the number of deaths per inhabitant, while local spatial association was strong only in Europe, the boxmap **(Picture 3)** shows that all areas identified with local dependence for the number of deaths per inhabitant were either HH (High-High) clusters in April or HL (High-Low) clusters after April, which means that in general locations with a high number of deaths were close to other areas that also had a high number of deaths. Even though April was a very concerning month to the international community, global spatial autocorrelation on the number of cases per inhabitant only started to grow higher than IM>0.50 in October, but the boxmaps for the number of infections show the same trend that happened for the number of deaths **(Picture 4)**, when looking them together with the *LISA* maps **(Picture 2)** all locations identified with spatial association were either HH or HL *clusters*.
